Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-06 ms.tex

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the order of magnitude difference between
$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
(Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due
to the variation in the Nuker stellar density profile $\Gamma$ at
fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate
to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Fig.~NICK).  The
combination of (1) and (2) is capable of explaining much of the
observed sample, especially considering that scatter in $L_{\rm X}$
due to variations in $\dot{M}$ is exacerbated by the expectation that
$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows.

>>>>

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the order of magnitude difference between
$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
(Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due
to the variation in the Nuker stellar density profile $\Gamma$ at
fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate
to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Fig.~NICK).  The
combination of (1) and (2) is capable of explaining much of the
observed sample, especially considering that scatter in $L_{\rm X}$
due to variations in $\dot{M}$ is exacerbated by the expectation that
$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows {\bf
  AG Challenge: Scatter in $L_X$ is similar for cores and cusps in Perllegrini}.
